\documentclass[12pt,letterpaper,sans]{moderncv} 
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[utf8]{inputenc}
\usepackage[]{geometry, amsfonts}
\geometry{verbose,tmargin=0.5in,bmargin=0.4in,lmargin=0.5in,rmargin=0.7in}
%---------LAST UPDATED: 05/23/26---------



%Info
\name{Vignesh}{Jagathese}
\title{Visiting Assistant Professor, NDSU}   
\phone[mobile]{(732)~447~3062}  
\email{vignesh.jagathese@ndus.edu}
\homepage{vigj.net}
\social[linkedin]{vignesh-jagathese}
%\social[orcid]{0000-0003-4665-9938}
\extrainfo{I am a US Citizen.}




\begin{document}
%Make title
\makecvtitle

\section{Academic Appointments}
\cventry{August 2026-}{Visiting Assistant Professor}{North Dakota State University (NDSU)}{}{}{} 
\section{Education}
\cventry{May 2026}{PhD, Mathematics}{University of Illinois Chicago (UIC)}{}{}{Advisor: \href{https://kftucker.people.uic.edu/home/}{Kevin Tucker}} 
\cventry{April 2020}{Masters of Science, Mathematics}{University of Michigan (UofM)}{}{}{} 
\cventry{April 2020}{Bachelor of Science, Honors Mathematics}{University of Michigan (UofM)}{}{}{} 
% arguments 3 to 6 can be left empty
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\section{Mathematical Interests}
\cvitem{}{Commutative Algebra, Algebraic Geometry, $F$-Singularities, Quasi-$F$-Splittings, $F$-Pure and Plus-Pure Thresholds, Singularities via Cartier Operators}



\section{Work Experience}
\cventry{2020-2021}{VECO Power Trading}{Quantitative Trader and Researcher}{}{}{Developed models to predict day ahead energy prices, written using R, PHP, MySQL and Python.}
\cventry{Summer 2019}{Chicago Trading Company}{Quantitative Trading Intern}{}{}{}

\cventry{2017-2018}{University of Michigan Solar Car Team}{Operations Director}{}{}{Led world class 50+ member student team,  managed \$1.5M manufacturing timeline.}


\section{Publications and Preprints}
\cventry{[3]}{Bounds on the plus-pure thresholds of some hypersurfaces in (ramified) regular rings}{(2026), with Marta Benozzo, Vaibhav Pandey, Pedro Ramirez Moreno, Karl Schwede, and Prashanth Sridhar}{\href{https://arxiv.org/abs/2509.07217}{2509.07217}, (\textit{\textbf{Mathematische Zeitschrift}}. to appear)}{}{}
\cventry{[2]}{On quasi-$\mathbf{F}$-purity of excellent rings}{(2026)}{\href{https://arxiv.org/abs/2503.10778v1}{2503.10778}}{(\textit{\textbf{Communications in Algebra}} 54 (4). 1760-1771 DOI: 10.1080/00927872.2025.2565687)}{}
\cventry{[1]}{On $\mathbf{F}$-pure thresholds and quasi-$\mathbf{F}$-purity of hypersurfaces}{(2025), with Jack J Garzella}{\href{https://arxiv.org/abs/2509.06211}{2509.06211}, Submitted}{}{}


\section{Awards and Grants}
 \cventry{2025}{UIC Award for Graduate Research}{}{}{The Graduate College’s longest-running support for research by graduate students at UIC. Comes with cash stipend}{}
\cventry{2023}{UIC Professor Herbert Alexander Award}{}{}{Awarded to exemplary graduate and undergraduate students within the MSCS department at UIC. Comes with cash stipend}{}
\cventry{2022-2026}{NSF RTG Fellowship}{}{Research and Training (pre-doctoral) Grant}{}{}
\cventry{Spring 2019}{NSF REU}{}{}{Research Experience for Undergraduates administered through UofM}{}




\newpage

\section{Teaching}
Undergraduate course descriptions at UIC can be found by clicking \href{https://catalog.uic.edu/ucat/course-descriptions/math/}{here}, and for UofM \href{https://lsa.umich.edu/math/undergraduates/undergraduate-math-courses/400-level-courses.html}{here}.
\begin{center}
   \begin{tabular}{|c|c|c|}
\hline

    \textbf{ \ \ \ Instructor of Record (UIC)  \ \ \ } & \textbf{ \ \ \ TA Appointments (UIC) \ \ \ } & \textbf{ \ Grading Positions (UofM) \ \ } \\
    \hline
     Math 109 (1 Cr, F-2022, S-2025) & Math 110 (F-2021, F-2022, S-2025) & Math 417 (W-2020) \\
    Math 090 (3 Cr, F-2023) & Math 105 (S-2023) & Math 452 (W-2019) \\
    Math 104 (1 Cr, S-2023) & Math 125 (F-2021) &  \\
    
\hline
\end{tabular} 
\end{center}
\cventry{Fall 2025}{Teaching Assistant Coordinator}{}{}{}{I worked with the Associate Head of Instruction to train and evaluate new TAs in the department.}


\section{Invited Talks}
\cventry{04/2026}{AMS Sectional at North Dakota State University: Topics in Commutative Algebra}{}{}{}{}
\cventry{02/2026}{University of Utah Commutative Algebra Seminar}{}{}{}{}
\cventry{01/2026}{JMM special session: Advances in Commutative Algebra}{}{}{}{}
\cventry{11/2025}{University of Missouri Algebra Seminar}{}{}{}{}
\cventry{10/2025}{University of Nebraska Commutative Algebra Seminar}{}{}{}{}
\cventry{09/2025}{Purdue Commutative Algebra Seminar}{}{}{}{}
\cventry{05/2025}{UC San Diego Algebraic Geometry Seminar}{}{}{}{}
\cventry{03/2024}{UIC Incoming Students Colloquium \textit{\small (Also 03/2025)}}{}{}{}{}
\cventry{01/2023}{UIC Graduate Student Colloquium \textit{\small (Also 04/2024, 01/2025)}}{}{}{}{}
\cventry{4/2022}{UIC Undergraduate Math Club  \textit{\small (Also 08/2023)}}{}{}{}{}

\section{Service}
\cventry{}{Journal Referee}{}{}{}{Refereed for Mathematische Zeitschrift.}
\cventry{2024-2025}{UIC Directed Reading Program Advisor}{}{}{}{
\begin{itemize}
    \item \textbf{(Spring 2025)} Advised statistics undergraduate Juan Garcia on introductory abstract algebra.
    \item \textbf{(Fall 2024) }Advised electrical engineering and physics undergraduate Caleb Williams on applications of category theory.
    \item \textbf{(Spring 2024)} Advised mathematics undergraduate Max Nguyen on sheaf cohomology, specifically on computations via the Čech complex.
\end{itemize}
}
\cventry{2023-2024}{UIC Commutative and Homological Algebra Graduate Seminar Organizer}{}{}{}{Founded and organized a graduate seminar on active research topics in algebra.}
\cventry{2022-2023}{UIC Mathematics Graduate Student Association Secretary}{}{}{}{}



\section{Outreach}
\cventry{2022-2026}{Math Circles of Chicago Teacher}{}{}{}{Taught weekend sessions and was an instructor for their summer programs in 2023 and 2026.}
\cventry{11/2024}{Sonia Kowalevsky Math Day Organizer}{}{}{}{Helped organize an annual outreach program to help spark young womens' interest in math.}
\cventry{Summer 2024}{Young Scholars Program Instructor}{}{}{}{Taught and helped organize a free summer program for Chicago high school students at UIC.}
\cventry{2018-2020}{Wolverine Pathways Instructor}{}{}{}{}
\cventry{4/2019}{MMaths Math Competition Organizer}{}{}{}{}

\clearpage 
\end{document}


%% end of file `template.tex'.

